### 2022-04-13 greta/mcmc.Rmd
10 replicates

sims <- purrr::map_dfr(1:100, \(i) simulate(), .id = "i")
sims |> ggplot(aes(t, N, group=i)) + geom_line(alpha=0.06)
```

@@

```{r}

library(scoringRules)

observed <- sims %>% filter(i == 1) %>% pull(N)
posterior_sims
dat <- posterior_sims |> pivot_wider(id_cols = "t", names_from="i", values_from = "N") |> select(-t) |> as.matrix()

score <- scoringRules::logs_sample(observed, dat)
logsscore <- score[-1] # drop first point
mean(logsscore)

score <- scoringRules::crps_sample(observed, dat)
crpsscore <- score[-1] # drop first point
mean(crpsscore)

>>>>

sims <- purrr::map_dfr(1:10, \(i) simulate(), .id = "i")
sims |> ggplot(aes(t, N, group=i)) + geom_line(alpha=0.06)
```

@@

First, a single 'observed' sample from the true:

```{r}
library(scoringRules)

scores <- function(observed, dat) {
  logsscore <- scoringRules::logs_sample(observed, dat)
  crpsscore <- scoringRules::crps_sample(observed, dat)
  data.frame(logs = mean(logsscore[-1]), crps =  mean(crpsscore[-1]))

}
# ensemble predictions
dat <- posterior_sims |> pivot_wider(id_cols = "t", names_from="i", values_from = "N") |> select(-t) |> as.matrix()

# Score just the 1st replicate "true" observations
observed <- sims |> filter(i == 1) |> pull(N)
scores(observed, dat)

```
```{r}
# score over all replicates:

rep_scores <- sims |> group_by(i) |> group_map(~ scores(.x$N, dat)) |> bind_rows()
```

```{r}
rep_scores |> summarise(across(.fns= base::mean))

library(patchwork)
ggplot(rep_scores) + geom_histogram(aes(crps)) + 
(ggplot(rep_scores) + geom_histogram(aes(logs)) )
